WSSSPE4-paper-reviewer-response

### 2017-12-18 WSSSPE4_report/WSSSPE4_paper.tex
minor changes in sections 2 and 4, more work in response.

Submissions to WSSSPE4 comprised
19 lightning talks,
4 idea papers,
3 position paper,
5 experience papers,
and
3 demos.
Most of the submissions were accepted, since the goal of WSSSPE is always to
take in as many relevant inputs as possible, and to encourage their authors to
participate in sharing and implementing their ideas.
% Specifically,
% 19 lightning talks,
% 4 idea papers,
% 3 position papers,
% 2 experience papers,
% and
% 3 demos
% were accepted, as mentioned in Section~\ref{sec:presentations}.
(Two of the submitted lightning talks and one submitted experience paper were rejected, while two more submitted experience papers
were accepted as lightning talks.)
The papers and lightning talks have been published as a volume in the CEUR Workshop Proceedings~\cite{WSSSPE4-proceedings}.

@@

WSSSPE4 included the presentation of 12 10-minute talks (based on four idea papers, three position papers,
two experience papers, and three demos) that addressed a wide range of topics around
sustainability for software in science. These talks covered three main areas.

% The following four papers belong to the first area: the academic environment.
%For talks with multiple authors, an
% \textsuperscript{\textasteriskcentered} indicates the author who presented the talk.
Four papers, 
% \begin{itemize}
% \item Michael Heroux: \emph{Idea paper: Sustainable \& Productive:
% Improving Incentives for Quality Software}
~\cite{Heroux:2016ws}, 
% \item Gabrielle Allen: \emph{Idea Paper: Establishing a Professional
% Society for Research Software}
~\cite{GAllen:2016ws}, 
% \item Olivier Philippe\textsuperscript{\textasteriskcentered}, Simon Hettrick, and Neil Chue Hong:
% \emph{Experience Paper: Preliminary analysis of a survey of UK Research
% Software Engineers}
~\cite{Philippe:2016ws}, and 
% \item Christopher Gwilliams: \emph{Demo: Using industrial engagement to
% create and develop research ties within academia}
~\cite{Gwilliams:2016ws} belong to the first area: the academic environment.
They address diverse aspects ranging from incentives for quality software to
advocating a professional society for research software to roles and degrees for
research software engineers.
%\end{itemize}
The second main area, concerned with characteristics and needs of
research software, includes five papers:
~\cite{Dubey1:2016ws},  ~\cite{ChueHong:2016ws},
~\cite{Dubey2:2016ws}, ~\cite{Queiroz:2016ws}, and ~\cite{Childers:2016ws}.
% \begin{itemize}
% \item Anshu Dubey\textsuperscript{\textasteriskcentered} and Katherine Riley: \emph{Experience Paper: Software
% Engineering and Community Codes Track in ATPESC}
% \item Neil Chue Hong: \emph{Position Paper: Why do we need to compare
% research software, and how should we do it?}
% \item Anshu Dubey\textsuperscript{\textasteriskcentered} and Lois Curfman McInnes: \emph{Idea Paper: The Lifecycle
% of Software for Scientific Simulation}
% \item Francisco Queiroz\textsuperscript{\textasteriskcentered} and Rejane Spitz: \emph{Position Paper:
% Collaborative Gamification Design for Scientific Software}
% \item Bruce Childers\textsuperscript{\textasteriskcentered}, Jack Davidson, Wayne Graves, Bernard Rous, and
% David Wilkinson: \emph{Position Paper: Active Curation of Artifacts is Changing
% the Way Digital Libraries will Operate}
% \end{itemize}
%\noindent 
Three contributions, ~\cite{Ganguly:2016ws}, ~\cite{Shende:2016ws},
and ~\cite{Sallai:2016ws} , focused on the third main area: elucidating lessons learned
from or visions for use cases of scientific software and communities working
with and\slash or on a software package. There were 19 lightning talks presented at WSSSPE4, (in order of
presentation): ~\cite{Sufi:2016ws}, ~\cite{Gesing:2016ws},
~\cite{Ram:2016ws}, ~\cite{Loffler:2016ws}, ~\cite{Katz:2016ws},
~\cite{Idaszak:2016ws}, ~\cite{Hwang:2016ws}, ~\cite{Goble:2016ws},
~\cite{Druskat:2016ws}, ~\cite{Contrastin:2016ws},
~\cite{AAllen:2016ws}, ~\cite{ChueHong:2016wsb},
~\cite{vanHage:2016ws}, ~\cite{GAllen:2016wsb}, ~\cite{Seidel:2016ws}, 
  ~\cite{Emsley:2016ws}, ~\cite{Dongarra:2016ws},
  ~\cite{Bauer:2016ws},  and ~\cite{Aldabjan:2016ws}.

>>>>

Submissions to WSSSPE4 comprised
19 lightning talks,
4 idea papers,
3 position paper,
5 experience papers,
and
3 demos.
Most submissions were accepted, since the goal of WSSSPE is always to
take in as many relevant inputs as possible, and to encourage their authors to
participate in sharing and implementing their ideas. Two submitted lightning talks and one submitted experience paper were rejected, while two more submitted experience papers
were accepted as lightning talks.
% Specifically,
% 19 lightning talks,
% 4 idea papers,
% 3 position papers,
% 2 experience papers,
% and
% 3 demos
% were accepted, as mentioned in Section~\ref{sec:presentations}.
%
The papers and lightning talks have been published as a volume in the CEUR Workshop Proceedings~\cite{WSSSPE4-proceedings}.

@@

WSSSPE4 included the presentation of 12 10-minute talks (based on four idea papers, three position papers,
two experience papers, and three demos) that addressed a wide range of topics around
sustainability for software in science. These talks covered three main areas.
%
% The following four papers belong to the first area: the academic environment.
%For talks with multiple authors, an
% \textsuperscript{\textasteriskcentered} indicates the author who presented the talk.
%Four papers %,  
% \begin{itemize}
% \item Michael Heroux: \emph{Idea paper: Sustainable \& Productive:
% Improving Incentives for Quality Software}
%~\cite{Heroux:2016ws}, 
% \item Gabrielle Allen: \emph{Idea Paper: Establishing a Professional
% Society for Research Software}
%~\cite{GAllen:2016ws}, 
% \item Olivier Philippe\textsuperscript{\textasteriskcentered}, Simon Hettrick, and Neil Chue Hong:
% \emph{Experience Paper: Preliminary analysis of a survey of UK Research
% Software Engineers}
%~\cite{Philippe:2016ws}, and 
% \item Christopher Gwilliams: \emph{Demo: Using industrial engagement to
% create and develop research ties within academia}
%~\cite{Gwilliams:2016ws} 
%belong to 
The first area was the academic environment, with four papers
that address diverse aspects ranging from incentives for quality software to
advocating a professional society for research software to roles and degrees for
research software engineers~\cite{Heroux:2016ws, GAllen:2016ws, Philippe:2016ws, Gwilliams:2016ws}.
%\end{itemize}
The second area was concerned with characteristics and needs of
research software and included five papers~\cite{Dubey1:2016ws, ChueHong:2016ws, Dubey2:2016ws, Queiroz:2016ws, Childers:2016ws}.
% \begin{itemize}
% \item Anshu Dubey\textsuperscript{\textasteriskcentered} and Katherine Riley: \emph{Experience Paper: Software
% Engineering and Community Codes Track in ATPESC}
% \item Neil Chue Hong: \emph{Position Paper: Why do we need to compare
% research software, and how should we do it?}
% \item Anshu Dubey\textsuperscript{\textasteriskcentered} and Lois Curfman McInnes: \emph{Idea Paper: The Lifecycle
% of Software for Scientific Simulation}
% \item Francisco Queiroz\textsuperscript{\textasteriskcentered} and Rejane Spitz: \emph{Position Paper:
% Collaborative Gamification Design for Scientific Software}
% \item Bruce Childers\textsuperscript{\textasteriskcentered}, Jack Davidson, Wayne Graves, Bernard Rous, and
% David Wilkinson: \emph{Position Paper: Active Curation of Artifacts is Changing
% the Way Digital Libraries will Operate}
% \end{itemize}
%\noindent 
%Three contributions, ~\cite{Ganguly:2016ws}, ~\cite{Shende:2016ws},
%and ~\cite{Sallai:2016ws} , focused on 
The third  area focused on elucidating lessons learned
from or visions for use cases of scientific software and communities working
with and\slash or on a software package, with three papers~\cite{Ganguly:2016ws, Shende:2016ws, Sallai:2016ws}.

In addition, 19 lightning talks were presented at WSSSPE4~\cite{Sufi:2016ws, Gesing:2016ws, Ram:2016ws, Loffler:2016ws, Katz:2016ws, Idaszak:2016ws, Hwang:2016ws, Goble:2016ws, Druskat:2016ws, Contrastin:2016ws, AAllen:2016ws, ChueHong:2016wsb, vanHage:2016ws, GAllen:2016wsb, Seidel:2016ws, Emsley:2016ws, Dongarra:2016ws, Bauer:2016ws, Aldabjan:2016ws}.

### 2017-12-18 WSSSPE4_report/jors-response.tex
minor changes in sections 2 and 4, more work in response.

``The APC is \pounds300 up to 8,000 words (approximately 12 pages including
figures and references). Additional APC charges will be \pounds10 for every
additional 750 words ($\approx$1 page).
So 16 pages would be \pounds340 - \pounds350. I would probably not be wanting to
go longer than 16 pages unless there was a good reason.''

Following these instructions, our initial submission had a body of 13 pages, an appendix of 2 pages, and 3 pages of references.

Nonetheless, we agree with the reviewers that this can be reduced, and have done so by removing the appendix and as advised by the reviewers, as further discussed below.  The revised version we are resubmitting has been reduced to \textcolor{red}{XX PAGES} of body, and 3 pages of references.

@@

\textcolor{red}{NEED TO ADDRESS}

@@

 In some places there is maybe detail which is not useful to the reader, for example detail of the survey responses.  I would recommend a shortened version of this article for publication but must reject it in its current format.
\end{quoting}

>>>>

``The APC is \pounds300 up to 8,000 words (approximately 12 pages including
figures and references). Additional APC charges will be \pounds10 for every
additional 750 words ($\sim$1 page).
So 16 pages would be \pounds340 - \pounds350. I would probably not be wanting to
go longer than 16 pages unless there was a good reason.''

Following these instructions, our initial submission had a body of 13 pages, an appendix of 2 pages, and 3 pages of references (as JORS publishes appendices as separate PDF attachments, and does not typeset them.)

Nonetheless, we agree with the reviewers that this can be reduced, and have done so by removing the appendix and as advised by the reviewers, as further discussed below.  The revised version we are resubmitting has been reduced to \textcolor{red}{11} pages of body, and 3 pages of references, a reduction of \textcolor{red}{5} of the original 18 pages.

\textcolor{red}{Can we remove 2 more pages?}

@@

We have removed the list of presentations.

@@

 In some places there is maybe detail which is not useful to the reader, for example detail of the survey responses.

\textcolor{red}{NEED TO RESPOND}

\begin{quoting}
I would recommend a shortened version of this article for publication but must reject it in its current format.
\end{quoting}
